COVID-19 Pandemic Influence on K1-12 Student Bullying Situation

### 2024-02-15 outputs/paper/paper.qmd
add title

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Mary Cheng
  - Shipeng Zhang
  - Yimiao Yuan
thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "COVID-19 Pandemic Influence on K1-12 Student Bullying Situation"
author: 
  - Mary Cheng
  - Shipeng Zhang
  - Yimiao Yuan
thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
